学術論文

### 2025-11-04 articles.Rmd
今日の作業
update

- [54] Matsumoto, K., Hamatani, S., Mizuno, Y., Maeno, A., Kasai, M., Watanabe, K., Kamashita, R., Sunami, N., Ikeda, M., Nagata, S., Inoue, M., Kimura, Y., Yokoo, M., Kunisato, Y., Akasaki, Y., Nakamura, M.(in press). Self-Help Cognitive Behavioral Therapy for Gaze Anxiety in Young Adults: Protocol of a 3-Arms, Multicenter, Randomized Controlled Trial. Psychiatry and Clinical Neurosciences Reports.

@@

>>>>

@@

- [54] Matsumoto, K., Hamatani, S., Mizuno, Y., Maeno, A., Kasai, M., Watanabe, K., Kamashita, R., Sunami, N., Ikeda, M., Nagata, S., Inoue, M., Kimura, Y., Yokoo, M., Kunisato, Y., Akasaki, Y., Nakamura, M.(2025). Self-Help cognitive behavioral therapy for gaze anxiety in young adults: Protocol of a 3-arms, multicenter, randomized controlled Trial. Psychiatry and Clinical Neurosciences Reports.2025;0:e70236. https://doi.org/10.1002/pcn5.70236
